The promise of community-driven preprints in ecology and evolution

### 2024-06-05 ms/ms.qmd
Some fixes

Our analysis has allowed us to better understand preprinting/postprinting practices in *EcoEvoRxiv*. Based on the insights from our analysis, we provide recommendations to authors on ways they can further promote open and transparent research:

@@

# Conflicts of Interest
The authors would like to awknowledge competing interests on the perspectives presented in this paper given that many are founding members of *EcoEvoRxiv* (DWAN, SN, ML) and/or are part of the *EcoEvoRxiv* committee.

>>>>

Our analysis has allowed us to better understand preprinting/postprinting practices in *EcoEvoRxiv*. In summary, *EcoEvoRxiv* articles are diverse but with primary research articles on vertebrates comprising most of the articles posted. North America, Europe and Australia use *EcoEvoRxiv* the most with very few non-English language articles to date. Earlier career researchers and submitting authors with 'male-associated names' tended to use *EcoEvoRxiv* the most. Articles posted to *EcoEvoRxiv* tend to take up to 8 months to become published with many articles not be open access. Code and data sharing was also relatively uncommon at the preprint stage. Based on the insights from our analysis, we provide recommendations to authors on ways they can further promote open and transparent research:

@@

# Conflict of Interest
The authors would like to awknowledge competing interests on the perspectives presented in this paper given that many are founding members of *EcoEvoRxiv* (DWAN, SN, ML) and/or are part of the *EcoEvoRxiv* committee.
